R for Clinical Study Reports and Submission

### 2022-09-20 slides/fda-workshop-slides.Rmd
update project information

- During the workshop, we will use `esubdemo` project.
  - `esubdemo` is shared in RStudio Cloud (<https://rstudio.cloud/>)
  - Project link will be shared at the beginning of the course.

@@

- R is widely used in visualization
  - [SafetyGraphics](https://github.com/SafetyGraphics/safetyGraphics)
  - [forestly](https://elong0527.github.io/forestly/articles/example.html#construct-interactive-forest-plot-1): [Interactive forest plot for DMC safety monitoring in clinical trials](https://rinpharma.com/publication/rinpharma_194/)

>>>>

- During the workshop, we will use `esubdemo` project.
  - `esubdemo` is shared in RStudio Cloud (<https://rstudio.cloud/>)
  - [Project link](https://rstudio.cloud/spaces/183786/join?access_code=FsVLtAUPS9s8uSc38ybNDTr3LYgFWWVq2OQjl8L4).

@@

- R is widely used in visualization
  - [metalite.table1](https://elong0527.github.io/metalite.table1/articles/metalite-table1.html): Interactive demographic table.
  - [forestly](https://elong0527.github.io/forestly/articles/forestly.html): Interactive forest plot for DMC safety monitoring in clinical trials
